---
title: "A clean and uncluttered template"

output:
  epuRate::epurate:
    toc: TRUE
    number_sections: FALSE
    code_folding: "hide"
---
<style>
#TOC {
  top: 1%;
  opacity: 0.5;
}
#TOC:hover {
  opacity: 1;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(epuRate)
library(rmarkdown)
```
  
<br><br>

> [R markdown](https://rmarkdown.rstudio.com) creates interactive reports from [R](https://www.r-project.org) code. This post provides a few tips I use on a daily basis to improve the appearance of output documents. In any case, an unavoidable resource is the [Rstudio documentation](https://rmarkdown.rstudio.com/html_document_format.html).



# Text formating {#text-formatting}
***
R markdown allows to easily format your text. You can add [links](www.r-graph-gallery.com), write in **bold** or *italic*. This is very well explained in the [Rstudio cheatsheet](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf).

Here is the code I used to make this paragraph:
```{r, eval=FALSE}
R markdown allows to easily format your text. You can add [links](www.r-graph-gallery.com), write in **bold** or *italic*. This is very well explained in the [Rstudio cheatsheet](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf).
```



# Horizontal lines {#horizontal-line}
***
Add an horizontal line by adding 3 stars:
```{r, eval=FALSE}
***
```

***



# Chapter auto numbering {#auto-numbering}
***
Header of level 1, 2, 3 are set using #, ## and ###. You can auto number your chapters using this option in the header:
```{r, eval=FALSE}
---
title: "Your title"
output: 
  html_document:
    number_sections: TRUE
---
# Title
## A subtitle
## Another subtitle
# Another title
```



# Skip a line {#skip-line}
***
I really like to add spaces in my document to give it a more uncluttered look. This is done using the `<br>` command. This `.rmd` code:
```{r, eval=FALSE}
A first sentence
<br><br><br><br>
A seconde sentence
```

will give this `html`output:

***

A first sentence
<br><br><br><br>
A seconde sentence

***

